\section*{Abstract}

A multi-fidelity Bayesian optimisation framework is applied to Ahmed body aerodynamics, minimising the objective $f_1 = C_d + \tfrac{1}{3}C_l$ (drag plus one-third downforce) over two geometric design variables: rear slant angle ($15$--$40^\circ$) and underbody diffuser angle ($0$--$20^\circ$). Low-fidelity evaluations use steady RANS (simpleFoam, $k$-$\omega$~SST) on the L2 mesh (${\sim}436$K half-domain cells, ${\sim}200$~s/solve); high-fidelity evaluations use the same solver on the L3 mesh (${\sim}912$K cells, ${\sim}500$~s/solve). A 30-point Phase~1 Latin Hypercube DoE screens four variables; Sobol sensitivity analysis eliminates nose radius and fixes ride height, reducing the active space to two dimensions. A 50-point Phase~2 DoE and 20 Bayesian optimisation iterations (Expected Improvement acquisition) identify the L2 surrogate optimum at $\alpha_\mathrm{slant}=32.5^\circ$, $\alpha_\mathrm{diff}=8.9^\circ$, $f_1=0.210$.

An L3 validation run at this point reveals a $\Delta C_l=+0.160$ fidelity gap (18\% objective degradation), motivating a Kennedy \& O'Hagan additive co-Kriging correction. Eight L3 anchor simulations spanning the full design space train correction Gaussian Processes $\delta_{C_d}(\mathbf{x})$ and $\delta_{C_l}(\mathbf{x})$. The corrections are spatially non-uniform ($\delta_{C_l}$ ranges $-0.114$ to $+0.167$), confirming that a constant bias correction would mis-locate the high-fidelity minimum. The corrected surrogate is re-optimised and the result verified with a single L3 solve.

The verified multi-fidelity optimum is $\alpha_\mathrm{slant}=38.9^\circ$, $\alpha_\mathrm{diff}=10.5^\circ$, $C_d=0.292$, $C_l=-0.285$, $f_1=0.198$ — a 5.7\% improvement over the L2 optimum and 20.2\% improvement over L3 evaluated at the old optimum location. Surrogate prediction error at the verified point is $0.6\%$, within the predicted $\pm2\sigma_\mathrm{HF}$ band. A $\lambda$-sensitivity sweep confirms the optimum location is robust for any positive downforce weighting. Basin-mapping L3 stencil solves confirm the optimum sits in a smooth basin, and resolve an anomalous L2 training point (BO iter~1, $f=0.642$) as a pseudo-time limit-cycle artefact that vanishes on the finer mesh. Total campaign cost: ${\sim}60$ CPU-hours.
